Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2024-11-26 README.qmd
Add official DOI

<!-- badges: start -->
[![Preprint](https://img.shields.io/badge/Preprint-10.31235%2Fosf.io%2Fy8ked-blue)](https://doi.org/10.31235/osf.io/y8ked) [![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FAQVNK-blue)](https://doi.org/10.17605/OSF.IO/AQVNK) [![Code DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.12817616.svg)](https://doi.org/10.5281/zenodo.12817616)
<!-- badges: end -->

@@

>>>>

@@

<!-- badges: start -->
[![Global Policy DOI](https://img.shields.io/badge/International%20Interactions%20DOI-10.1080%2F03050629.2024.2413965-brightgreen)](https://doi.org/10.1080/03050629.2024.2413965) [![Preprint](https://img.shields.io/badge/Preprint-10.31235%2Fosf.io%2Fy8ked-blue)](https://doi.org/10.31235/osf.io/y8ked) [![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FAQVNK-blue)](https://doi.org/10.17605/OSF.IO/AQVNK) [![Code DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.12817616.svg)](https://doi.org/10.5281/zenodo.12817616)
<!-- badges: end -->

> Suparna Chaudhry, Audrey L. Comstock, and Andrew Heiss, “Pandemic Pass? Treaty Derogations and Human Rights Practices during COVID-19,” *International Interactions* 50, no. 6 (2024): 1064–86, <https://doi.org/10.1080/03050629.2024.2413965>.
